### 2019-06-04 manuscript.tex
Some changes to modelling
Sorting out some of the analysis for the probability matching experiment

\paragraph{} We may often find ourselves with multiple tasks to complete but limited resources with which to complete them. For example, with in upcoming exam, students will often have a large amount of material to cover but only a limited amount of time to spend revising the subjects. How a student should divide up their time depends on how well prepared they are. A well prepared student would probably benefit from covering each topic an equal amount as they are already likely to succeed. On the other hand, a poorly prepared student may benefit from spending all their time on a subset of topics and hope that the topics they revised for come up. %Exams often require that the student has a reasonable level of knowledge about all possible topics that may appear. However, often there can be a wide range of topics that are not always so easy to link and thus appear entirely separate. Some students may struggle with the topics that are going to come up, whereas others might be very confident in their chances of succeeding regardless of what actually appears in the exam questions. For these two hypothetical students, it does not make sense for them to approach these situations with the same strategy. The student that is already fairly confident would benefit more from dividing their time relatively equally across the subjects that may come up because they are already fairly prepared. However, the student with little knowledge may not be able to reach a suitable level of preparedness for the exam if they were to split their time. Instead, for this student, it may be more beneficial to instead be more selective in what they study and primarily focus on one topic in the hope that topic will be in the exam.

\paragraph{} Implementing this logic may seem fairly straightforward; if every task is difficult, it is a good idea to focus on only a subset, whereas when the tasks are straightforward, it makes sense to instead attempt a larger number. However, in tasks that present scenarios in which this logic should be applied,  people demonstrate an inability to switch from attempting both goals in an easy context, to focussing on one when they are both difficult \citep{clarke2015failure,morvan2012human}. By not following this relatively simple logic, the rate of success can fall far below that which would be expected should the optimal strategy have been implemented.

\paragraph{} Some theories assume that people generally aim to make decisions that offer the greatest expected utility \citep{mongin1997expected}. However, problems can become intractable as the number of possible outcomes to compare grows \citep[see ][ for a discussion of this]{BOSSAERTS2017917}. Therefore, when thinking of optimal decisions, one must take into account the limitations of the individual. This is termed Bounded Rationality \citep{simon1990invariants} and posits that people do make optimal decisions given some limitations.

@@

\paragraph{} When it comes to smaller problems, it is feasible to implement a strategy that compares the expected outcome across multiple choices. However, \cite{KahnemanProspect} present evidence that suggests that this is not the case either. In their work, they presented people with two choices; \textit{Option A} offered participants a $50\%$ chance to win \$1000 and a $50\%$ to win nothing, and \textit{Option B} would give them \$450 for certain. Using the EUT, Option A is the better option as this would on average reward the participant \$500. However, this was not the observed pattern of behaviour for most participants who instead would opt for \textit{Option B}. Perhaps more interestingly, they found that framing problems such as these would result in a shift from the sure option, to the more "risky" option. When framing this decision as being a loss rather than a gain, participants would instead opt for \textit{Option A} which in this context would be the worst option as it offers the greatest average loss. It can be argued that since the choices people make can be altered by simply changing the way a problem is framed, we are not simply comparing options and choosing the one that offers the best outcome \citep{KahnemanChoicesValuseFrames}, and instead we are incorporating information that is not relevant to the decision being made.

\paragraph{} The issue with these sorts of tasks is that they are hypothetical \citep{KahnemanProspect}. Participants are supposed to imagine they are in a situation where choosing either option would result in one of the two stated outcomes. The question arises; what if people are put in a situation in which they are making decisions with actual outcomes? Until this point, the tasks considered have been hypothetical and are rarely (if ever) encountered in everyday life. As such, it would make more sense to look at decisions that people make many times a day.

>>>>

\paragraph{} We often find ourselves with multiple tasks to complete but limited resources with which to complete them. For example, University students typically have a large amount of material to remember, limited amount of time to spend preparing, and uncertainty around what questions they will be asked. How a student should divide up their time depends on how much time is available. A student preparing well in advance would probably benefit most from studying each topic for an equal amount of time ensuring they are fully prepared for any questions. A student who leaves it to the last minute, however, might need to strategically focus their efforts on a subset of the material and hope that the topics they revised for come up. %Exams often require that the student has a reasonable level of knowledge about all possible topics that may appear. However, often there can be a wide range of topics that are not always so easy to link and thus appear entirely separate. Some students may struggle with the topics that are going to come up, whereas others might be very confident in their chances of succeeding regardless of what actually appears in the exam questions. For these two hypothetical students, it does not make sense for them to approach these situations with the same strategy. The student that is already fairly confident would benefit more from dividing their time relatively equally across the subjects that may come up because they are already fairly prepared. However, the student with little knowledge may not be able to reach a suitable level of preparedness for the exam if they were to split their time. Instead, for this student, it may be more beneficial to instead be more selective in what they study and primarily focus on one topic in the hope that topic will be in the exam.

\paragraph{} Implementing this logic may seem fairly straightforward; if the demands of combined tasks exceed the available resources, it is a good idea to focus on only a subset, whereas when the tasks are straightforward and resources abundant, it makes sense to instead attempt the full set. However, in experiments that present scenarios in which this logic should be applied,  people demonstrate an inability to switch from attempting both goals in an easy context, to focussing on one when they are both difficult \citep{clarke2015failure,morvan2012human}. By not following this relatively simple logic, the rate of success can fall far below that which would be expected should the optimal strategy have been implemented.

\paragraph{} Some theories assume that people generally aim to make decisions that offer the greatest expected utility \citep{mongin1997expected}. However, problems can become intractable as the number of possible outcomes to compare grows \citep[see ][ for a discussion of this]{BOSSAERTS2017917}. Therefore, when thinking of optimal decisions, one must take into account the limitations of the individual. This is termed Bounded Rationality \citep{simon1990invariants} and posits that people make decisions that are optimal given their limitations; in other words, when people make decisions that appear sub-optimal, this can usually be explained by limitations on cognitive systems like memory and attention.

@@

\paragraph{} When it comes to simple problems, it could be feasible to estimate the expected outcome across multiple choices and select the best outcome. However, \cite{KahnemanProspect} present evidence that suggests that even when these outcomes are simple to calculate, people often make choices that do not maximise expected utility. In their work, they presented people with two choices; \textit{Option A} offered participants a $50\%$ chance to win \$1000 and a $50\%$ to win nothing, and \textit{Option B} would give them \$450 for certain. Using the EUT, Option A is the better option as this would on average reward the participant \$500. However, this was not the observed pattern of behaviour for most participants who instead would opt for \textit{Option B}. At first glance this may seem consistent with risk aversion, a long-established tendency to prefer a sure gain over an uncertain one \citep{KAHNEMAN1972430}.

\paragraph{} But \cite{KahnemanProspect} found that framing problems as being a loss rather than a gain led participants to instead opt for \textit{Option A}. That is, people choose a 50\% chance to lose \$1000, over a sure loss of \$450 even though now the expected utility of Option B is actually higher. By showing that the choices people make can be altered by simply changing the way a problem is framed, \cite{KahnemanChoicesValuseFrames} demonstrate that we are not simply comparing options and choosing the one that offers the highest utility.

\paragraph{} The choice problems used to evaluate the strengths and shortcomings of human decisions are often abstract and hypothetical. Participants are supposed to imagine they are in a situation where choosing either option would result in one of the two stated outcomes. What if people are put in a situation in which they are making decisions with actual outcomes? One might expect the concrete and routine decisions that people make many times a day to be more optimal.
